PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-08 paper/ms.tex
update paper

%
% key authors:
%
\author[0000-0002-0514-5538]{L.\,G.\,Bouma}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J.\,N.\,Winn}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
% PENDING
%\author[0000-0001-7246-5438]{A. Vanderburg}
%\affiliation{Department of Astronomy, The University of Texas at
%Austin, Austin, TX 78712, USA}
%\affiliation{NASA Sagan Fellow}

% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%CONFIRMED
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%CONFIRMED
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%PENDING
\author{S. Seager} % seager@mit.edu
\affiliation{Department of Earth, Atmospheric, and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%     Karen Collins karenacollins@outlook.com
%     Sam Quinn squinn@cfa.harvard.edu
%     Dana Louie danalouie@astro.umd.edu
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

@@

%PENDING
\author{J. P. Doty} % jpd@noqsi.com
\affiliation{Noqsi Aerospace Ltd., 15 Blanchard Avenue, Billerica, MA,
01821, USA}

% PENDING
\author{D. Louie} % danalouie@astro.umd.edu
\affiliation{University of Maryland, Baltimore County, 1000 Hilltop
Circle, Baltimore, MD 21250, USA}

% PENDING
\author[0000-0002-8964-8377]{S. N. Quinn} % squinn@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

%PENDING
\author[0000-0003-4724-745X]{M. E. Rose} %  mark.rose@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

%PENDING
\author[0000-0002-6148-7903]{J. C. Smith} % jeffrey.c.smith-1@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
\affiliation{SETI Institute, Mountain View, CA 94043, USA}

%PENDING
\author{J. Villase\~nor} % jsvilla@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}

@@

The 2-minute stacks for \ptfo\ were reduced to lightcurves by the
Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
pixels chosen to maximize the SNR of the total flux of the target
\citep{smith_kepler_apertures_2017}.  Non-astrophysical variability
was removed by fitting out trends common to many stars
\citep{smith_kepler_PDC_2017}.

>>>>

%
% key authors:
%
\author[0000-0002-0514-5538]{L.\,G.\,Bouma}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J.\,N.\,Winn}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%CONFIRMED
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
%
%PENDING yy
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
%
%CONFIRMED
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%CONFIRMED
\author[0000-0002-6892-6948]{S.~Seager} % seager@mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
\affiliation{Department of Earth, Atmospheric and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\affiliation{Department of Aeronautics and Astronautics, MIT, 77
Massachusetts Avenue, Cambridge, MA 02139, USA}
%
%PENDING yy
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%     Karen Collins karenacollins@outlook.com
%     Sam Quinn squinn@cfa.harvard.edu
%     Dana Louie danalouie@astro.umd.edu
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

@@

%CONFIRMED
\author{J. P. Doty} % jpd@noqsi.com
\affiliation{Noqsi Aerospace Ltd., 15 Blanchard Avenue, Billerica, MA,
01821, USA}

% PENDING yy
\author{D. Louie} % danalouie@astro.umd.edu
\affiliation{University of Maryland, Baltimore County, 1000 Hilltop
Circle, Baltimore, MD 21250, USA}

%CONFIRMED
\author[0000-0002-8964-8377]{S. N. Quinn} % squinn@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

%PENDING y
\author[0000-0003-4724-745X]{M. E. Rose} %  mark.rose@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

%PENDING y
\author[0000-0002-6148-7903]{J. C. Smith} % jeffrey.c.smith-1@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
\affiliation{SETI Institute, Mountain View, CA 94043, USA}

%CONFIRMED
\author{J. Villase\~nor} % jsvilla@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}

@@

The 2-minute stacks for \ptfo\ were reduced to lightcurves by the
Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
pixels chosen to maximize the SNR of the total flux of the target
\citep{smith_finding_2016}.  Non-astrophysical variability
was removed by fitting out trends common to many stars
\citep{smith_kepler_2012,stumpe_multiscale_2014}.
% \citep{smith_kepler_PDC_2017}
% \citep{smith_kepler_apertures_2017}
